Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-11 vesicle_code/docs/adhesion/adhesion.tex
changes by yny on Feb 11

\title{Adhesion, hydrodynamics and rheology of vesicle doublets}
% Force line breaks with \\
%\thanks{A footnote to the article title}%

@@

In our formulation we did not include any electrostatic interactions
between membranes under adhesion. When the electrostatic interaction is
important, an electro-osmotic pressure in the thin film is found to be
responsible for the observed membrane
undulation~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.

Future work includes three dimensional simulations, viscosity contrast,
dense suspensions, and confined suspensions.
Figure~\ref{fig:relaxationManyVes} shows an initial condition of five vesicles
suspended inside of a larger vesicle, and the configuration and
streamlines at an intermediate configuration.  There is no imposed flow, so the
dynamics are governed entirely by the adhesion, bending, and tension
forces.  In the absence of confinement, we would expect the vesicles to
align themselves as a rouleaux with the membranes forming a parachute,
male-female, or S-shape
configurations~\cite{FlormannAouane2017_SciReports}.  However, because
of the bounding vesicle and the dense packing, the interior vesicles
align themselves differently.  In addition, several parts of the
bounding membrane closely follow the interior membranes in order to
minimize the adhesion energy.   We also plot the tension (thrid) and
adhesion (fourth) of the final equilibrium configuration.  Both the
vesicle shape, tension, and adhesion qualitatively agree with our
doublet results.  In particular, the interior vesicles form a flat
contact region with a large negative tension.

@@

\begin{figure}[htp]
\centering
\includegraphics[height=0.24\textwidth,trim={10cm 0cm 10cm 0cm},clip]{figs/relaxationManyVesInitialCondition.png}
\includegraphics[height=0.24\textwidth,trim={2cm 0cm 2cm 0cm},clip]{figs/relaxationManyVesStreamlines.png}
\includegraphics[height=0.24\textwidth,trim={2cm 0cm 1cm 0cm},clip]{figs/relaxationManyVesTension.png}
\includegraphics[height=0.24\textwidth,trim={2cm 0cm 2cm 0cm},clip]{figs/relaxationManyVesAdhesion.png}
\caption{\label{fig:relaxationManyVes} Five vesicles in a quiescent flow
suspended in a bounding vesicle.   All vesicles are interacting through
an adhesion potential with Hamaker constant $\mathcal{H} = 0.7$ and
separation distance $\delta = 0.4$.  From left to right, the plots are
the initial condition, streamlines and an intermediate time, tension at
the steady-state configuration, and the adhesion force projected onto
the outward unit normal at the steady-state configuration.  Along the
bounding vesicle, the tension is largest and the adhesion is smallest in
the regions that are well-separated from the interior vesicles.  Similar
to other simulations, the interior vesicles are relatively flat and have
a large negative tension in the contact regions.}
\end{figure}

>>>>

\title{Hydrodynamics and rheology of adhesive vesicle doublets}
% Force line breaks with \\
%\thanks{A footnote to the article title}%

@@

In our formulation we did not include any electrostatic interactions
between membranes under adhesion. When the electrostatic interaction is
important, an electro-osmotic pressure in the thin film is found to be
responsible for the observed membrane
undulation~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.
In addition, simulations presented in this work are for identical vesicles (same reduced area, length, and
bending rigidity modulus) in the doublet. Flormann {\it et al.} demonstrated that asymmetric vesicle reduced area
may lead to various equilibrium doublet shape such as male-female, asymmetric S-shape and parachute shape.
It is also possible that viscosity contrast may also lead to slightly different equilibrium doublet shape.
Future work includes three dimensional simulations, dispersive vesicle properties (such as
reduced area and bending modulus), viscosity contrast, and effects of confinement on adhesive interactions.

Flormann {\it et al.} studied the clustering and packing of vesicles in free suspension~\cite{FlormannAouane2017_SciReports}. 
In engineering applications of vesicle emulsions
often smaller vesicles are enclosed in a big vesicle, as shown in 
Figure~\ref{fig:relaxationManyVes}, where  the left panel shows an initial condition of five vesicles
suspended inside of a larger vesicle.
The second panel from left shows the membrane configuration and flow
streamlines at an intermediate time.  There is no imposed flow, so the
dynamics are governed entirely by the adhesion, bending, and tension
forces.  In the absence of confinement, we would expect the vesicles to
align themselves as a rouleaux with the membranes forming a parachute,
male-female, or S-shape
configurations~\cite{FlormannAouane2017_SciReports}.  However, because
of the bounding vesicle and the dense packing, the interior vesicles
align themselves differently.  In addition, several parts of the
bounding membrane closely follow the interior membranes in order to
minimize the adhesion energy.   As a result of force balance the equilibrium shape of the bounding vesicle
is far from a symmetric shape while the interior smaller vesicles are of similar shape to each other.
We also plot the tension (thrid) and
adhesion (fourth) of the final equilibrium configuration.  
We remark that the adhesion force is all attractive on all the vesicle membranes while large positive
membrane tension is found only on the bounding vesicle. 
%Both the
%vesicle shape, tension, and adhesion qualitatively agree with our
%doublet results.  
In particular, the interior vesicles form a flat
contact region with a large negative tension.
We are now conducting simulations of such vesicle configuration under a planar shear flow.

@@

\begin{figure}[htp]
\centering
\includegraphics[height=0.24\textwidth,trim={10cm 0cm 10cm 0cm},clip]{figs/relaxationManyVesInitialCondition.png}
\includegraphics[height=0.24\textwidth,trim={2cm 0cm 2cm 0cm},clip]{figs/relaxationManyVesStreamlines.png}
\includegraphics[height=0.24\textwidth,trim={2cm 0cm 1cm 0cm},clip]{figs/relaxationManyVesTension.png}
\includegraphics[height=0.24\textwidth,trim={2cm 0cm 2cm 0cm},clip]{figs/relaxationManyVesAdhesion.png}
\caption{\label{fig:relaxationManyVes} Five vesicles in a quiescent flow
suspended in a bounding vesicle.   All vesicles are interacting through hydrodynamic flow and
an adhesion potential with Hamaker constant $\mathcal{H} = 0.7$ and
separation distance $\delta = 0.4$.  From left to right, the plots are
the initial condition, streamlines and an intermediate time, tension at
the steady-state configuration, and the adhesion force projected onto
the outward unit normal at the steady-state configuration.  Along the
bounding vesicle, the tension is largest and the adhesion is smallest in
the regions that are well-separated from the interior vesicles.  Similar
to other simulations, the interior vesicles are relatively flat and have
a large negative tension in the contact regions.}
\end{figure}
